---
title: "Rautahat Bara Sarlahi"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(dplyr)
library(kableExtra)
library(formattable)
library(knitr)
opts_chunk$set(echo = FALSE)

Land_18_19 <- read.csv("~/R/Rautahat.Bara.Sarlahi/data/Land_18_19.csv")
lands_I_18_19 <- read.csv("~/R/Rautahat.Bara.Sarlahi/data/lands_I_18_19.csv")
```


---  

4.0 LAND 

5.0 AGRICULTURE 

6.2 WEM

7.0 PROCUREMENT
 

 



##  Land

&nbsp;


Table 1: Total Ownland Cultivated [4.4]
```{r total_ownland_cultivated, echo=FALSE}

dt <-tribble(~" " ,~N,~mean,~N,~mean,2018,105,3.74,24,5.36, 2019,95,3.59,22,7.05)

kable(dt, "latex", booktabs = T, align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%
row_spec(0, font_size= 8) %>% 
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
&nbsp;

&nbsp;

Table 2: Total Land Cultivated [4.8]
```{r  total_land_cultivated, echo=FALSE}

dt2 <-tribble(~" " ,~N,~mean,~N,~mean,2018,105,3.99,24,5.46,2019,95,3.66,22,7.07)

kable(dt2, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%row_spec(0, font_size= 8) %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
&nbsp;

&nbsp;

Table 3: Crop Intensity [4.0]
```{r   Crop Intensity, echo=FALSE}

dtci <-tribble(~" ",~N,~mean,~N,~mean,2018,105,"206%",24,"204%" ,2019,95,"194%",22,"185%")
kable(dtci, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%row_spec(0, font_size= 8) %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
&nbsp;

&nbsp;

## Irrigation

> Iirrigated area in acre

> Irrigation in hours

>Irrigation intensity

&nbsp;

__Iirrigated area in acre__  
the average irrigated area in acre for a farmer in a year

Table 4: Irrigated Out Of Total Land Cultivated (In ha) [4.9]
```{r irrigated_out_of [4.9] , echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
Table_4 <- Land_18_19%>% 
  filter(total_land_cultivated_year>0) %>%
  group_by(year,TreatmentControl, household_questionnaire_id) %>%
  summarise(irrigated=sum(irrigated_out_of_tot_land_cult)*0.0338) %>% 
  group_by(year, TreatmentControl) %>%
  summarise(N=n(), irrigated=mean(irrigated))

dt2 <-tribble(~" " ,~N,~mean,~N,~mean,2018,105,2.48,24,3.94,2019,95,3.21,22,5.13)

kable(dt2, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

HH <-tribble(~" " ,~"Control" , ~"Treatment",2018,98,24,2019,95,21)


```
&nbsp;

&nbsp;

__Irrigation in Hours__  
number of hours by year an season&nbsp;

Table 5 : Time to irrigate 1 ha [6.21]  
```{r  irrigate 1 ha [6.21], echo=FALSE}

dtwem <-tribble(~" " ,~N,~mean,~N,~mean,2018,107,24,30,21,2019,100,16,30,32)

kable(dtwem, "latex", booktabs = T,align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
&nbsp;

Table 6: By year [5.0]
```{r irri By year [5.0], echo=FALSE}

dt2 <-tribble(~" " ,~N ,~"mean 1 ha" ,~"Total",~N ,~"mean 1 ha" ,~"Total" ,2018,107,28.0,348,26,21.6,244,2019,95,26.0,396,21,22.2,456)

kable(dt2, "latex", booktabs = T,align = "lcccccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:7, width = "1.5cm",border_left = F) %>%column_spec(4,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 1, "Control" = 3, "Treatment" = 3), bold = F, align = "c")

```
&nbsp;

&nbsp;


Table 7: By seasons [5.0]

```{r irri By seasons [5.0], echo=FALSE,message=FALSE, warning=FALSE, paged.print=FALSE}
Agriculture_18_19 <- read.csv("~/R/Rautahat.Bara.Sarlahi/data/Agriculture_18_19.csv")

c <- Agriculture_18_19 %>% filter(season_of_crop!="Annual") %>% 
  group_by(year,season_of_crop,TreatmentControl,household_questionnaire_id) %>%
  summarise(hr_per_ha=mean(hrs_irr_1katha)/0.0339,irrigate_hr=sum(irri_for_season))%>% 
  group_by(TreatmentControl,season_of_crop,year) %>%
  summarise(n=n(),average_hr_per_ha=mean(hr_per_ha,na.rm = T),
            total_irrigate_hr=mean(irrigate_hr,na.rm = T)) %>% 
  mutate(across(is.numeric, round, 2))

cc <- c[1:6,]
ct <- c[7:12,4:6]
cx <- cbind(cc,ct)[,-1]


kable(cx, "latex",col.names = c("Season","Year","N","mean 1 ha","Total","N","mean 1 ha","Total"), booktabs = T,align = "lcccccc",linesep = "") %>%
column_spec(1, bold = T) %>%
collapse_rows(columns = 1, valign = "top") %>% 
kable_styling(latex_options = "striped", position = "left") %>% 
column_spec(1:7, width = "1.5cm",border_left = F) %>%column_spec(5,border_right = T ,width = "1.5cm") %>%  row_spec(0, font_size= 9) %>% 
add_header_above(c(" " = 2, "Control" = 3, "Treatment" = 3), bold = F, align = "c")
  
```


__Irrigation Intensity__  
jdhffgbv ivugosi idnsgvysg indvs 

Table 7: by year[4.0]
```{r year irri_intensity [4.0], echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

irri_inten_y <- Land_18_19 %>% filter(total_land_cultivated_year>0,season!="Annual") %>% 
  group_by(TreatmentControl,year,household_questionnaire_id) %>%
  summarise(gross_irri=sum(irrigated_out_of_tot_land_cult),gross_crop=sum(total_land_cultivated),ii=gross_irri/gross_crop*100) %>% 
  filter(ii>= 0,ii<=100) %>% 
  group_by(TreatmentControl,year) %>% 
    summarise(N=n(),Mean=mean(ii)) %>% 
    mutate(across(is.numeric, round, 2)) 

iyc <- irri_inten_y[1:2,]
iyt <- irri_inten_y[3:4,3:4]
iyc_iyt <- cbind(iyc,iyt)[,-1]

kable(iyc_iyt, "latex",col.names = c("Year","N","Intensity","N","Intensity"), booktabs = T,align = "lcccc",linesep = "") %>%
  column_spec(1, bold = T) %>%
  kable_styling(latex_options = "striped", position = "left") %>% 
  column_spec(1:5, width = "1.5cm",border_left = F) %>%
  column_spec(3,border_right = T ,width = "1.5cm") %>%
  row_spec(0, font_size= 9) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

 

```

Table 9: by season [4.0]
```{r seasons irri_intensity [4.0], echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

irri_inten_s <- Land_18_19 %>% filter(total_land_cultivated_year>0,season!="Annual") %>% 
  mutate(irrigation_intens=irrigated_out_of_tot_land_cult/total_land_cultivated*100) %>% 
  filter(irrigation_intens>= 0,irrigation_intens<=100) %>% 
  group_by(TreatmentControl,season,year) %>% 
  summarise(N=n(), Mean= mean(irrigation_intens)) %>% 
  mutate(across(is.numeric, round, 2))

iic <-irri_inten_s[1:6,]
iit <- irri_inten_s[7:12,4:5]
iic_iit <- cbind(iic,iit)[,-1]

kable(iic_iit,col.names = c("Season","Year","N","mean","N","mean"), booktabs = T,align = "llcccc",linesep = "") %>%
  column_spec(1, bold = T) %>%
  kable_styling(latex_options = "striped", position = "left") %>% 
  column_spec(1:6, width = "1.5cm") %>%
  column_spec(4,border_right = T ,width = "1.5cm") %>% 
  collapse_rows(columns = 1, valign = "top") %>% 
  row_spec(0, font_size= 9) %>% 
  add_header_above(c(" " = 2, "Control" = 2, "Treatment" = 2), bold = F, align = "c")
  
```

# Frequency of households who irrigate [4.9]	
df <- Land_18_19 %>% filter(irrigated_out_of_tot_land_cult>0,season!="Annual") %>% 
  group_by(TreatmentControl,season,year) %>% count()

## fuel use
Table 10:Total litres of diesel/kerosene consumed for agriculture pumps in a YEAR [7.16] 
```{r fuel use Year [7.16], echo=FALSE}

dt <-tribble(~" " ,~N,~mean,~N,~mean,2018,71,362,25,622, 2019,46,146,16,385)

kable(dt, "latex", booktabs = T, align = "lcccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(1:5, width = "1.5cm",border_left = F) %>% column_spec(3,border_right = T ,width = "1.5cm") %>%
add_header_above(c(" " = 1, "Control" = 2, "Treatment" = 2), bold = F, align = "c")

```
1 Control           2018    71          362.3 Treatment         2018    25          622.

2 Control           2019    46          146.4 Treatment         2019    16          385.



&nbsp;


Table 11:# fuel use by the 'Water_extraction_mechanism'files- [6.2] 
```{r fuel use Season & Year  [6.2] , echo=FALSE}

fuel_wem <-tribble(~" " ,~N,~Summer,~Monsoon,~Winter,~Yearly,~N,~Summer,~Monsoon,~Winter,~Yearly,2018,71,121,94,61,276 ,27,160,140,170,470, 2019 ,56,42,7,40,89 ,28,136,55,71,262)

kable(fuel_wem, "latex", booktabs = T, align = "lcccccccccc",linesep = "") %>%
kable_styling(latex_options = "striped", stripe_index = 2,position = "left") %>% 
column_spec(2:11, width = "1cm",border_left = F) %>% column_spec(6,border_right = T ,width = "1cm") %>%
add_header_above(c(" " = 1, "Control" = 5, "Treatment" = 5), bold = F, align = "c")

```
  TreatmentControl  year Monsoon Summer Winter  Year
  <chr>            <dbl>   <dbl>  <dbl>  <dbl> <dbl>
1 Control           2018   107.   149.   239.   339.
2 Control           2019    66.7   98.5   50.3  108.
3 Treatment         2018   171.   180.   229.   507.
4 Treatment         2019   119.   292.   124.   458.


## aquaculture

Table 12 : land_for_aquaculture_ponds [4.1c]

```{r}


lands_I_18_19 %>% filter(land_for_aquaculture_ponds> 0,land_for_aquaculture_ponds<300) %>% 
  group_by(TreatmentControl,year) %>% 
  summarise(N=n(),Mean= mean(land_for_aquaculture_ponds,na.rm = T)*0.0339)
```

