---
title: "Sugarcane Irrigation Methods Report"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(readxl)
library(gridExtra)  # for arranging plots
library(grid)       # already included in R


df12_sugarcane <- read_excel("C:/Users/Dan/OneDrive - mail.tau.ac.il/NETAFIM_2024/df12_sugarcane.xlsx")
df2_sugarcane <- read_excel("C:/Users/Dan/OneDrive - mail.tau.ac.il/NETAFIM_2024/df2_sugarcane.xlsx")
crop_bind <- read_excel("C:/Users/Dan/OneDrive - mail.tau.ac.il/NETAFIM_2024/crop_bind.xlsx")
economy <- read_excel("C:/Users/Dan/OneDrive - mail.tau.ac.il/NETAFIM_2024/economy.xlsx")

```



```{r freq,acre,total}

p1 <- df12_sugarcane %>% 
  count(ir_method) %>% 
  ggplot(aes(x = ir_method, y = n, fill = ir_method)) + 
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = n),color = "black", vjust = 9,size = 4) +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  labs(title="Number of Households \nby Irrigation Methods",x="",y="No. of HH",fill="") + 
  theme_minimal(base_family = "serif")+theme(legend.position = "none")

ci_summary <- df12_sugarcane %>%
  select(ir_method, acre_sugarcane, plots_sugarcane) %>% 
  rename(`Total Sugarcane Acre`= acre_sugarcane, 
         `Total Sugarcane Plots`= plots_sugarcane) %>% 
  pivot_longer(cols = -ir_method, names_to = "variable", values_to = "value") %>%
  group_by(ir_method, variable) %>%
  summarise(mean = mean(value, na.rm = TRUE),
    sd = sd(value, na.rm = TRUE),n = sum(!is.na(value)),se = sd / sqrt(n),
    ci_lower = mean - 1.96 * se,ci_upper = mean + 1.96 * se,.groups = "drop") 


p2 <- ggplot(ci_summary, aes(x = ir_method, y = mean, fill = ir_method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = paste0(round(mean, 2))), vjust = 9,size = 4  ) +
  facet_wrap(~variable, scales = "free_y") +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  labs(title = "", x = "", y = "", fill = "") +
  theme_minimal(base_family = "serif")+ 
  theme(legend.position = "none")


grid.arrange(p1, p2, ncol = 2, widths = c(1, 2))
```

<br><br><br>

## Water Source

```{r water_source}

water_source <- 
  df12_sugarcane %>%
  select(ir_method, "ir_source", "ir_source_own_or_public") %>%
  pivot_longer(-ir_method, names_to = "variable", values_to = "value") %>%
  group_by(ir_method, variable, value) %>%
  summarise(count = n(), .groups = "drop_last") %>%
  group_by(ir_method, variable) %>%
  mutate(freq_percent = round(100 * count / sum(count), 1)) %>%
  arrange(ir_method, variable, desc(freq_percent))


##### [ir_source]
ir_source_colors <- c("skyblue", "skyblue2", "skyblue3", "skyblue4" )
p1_source <- water_source %>%
  filter(variable == "ir_source") %>%
  ggplot(aes(x = ir_method, y = freq_percent, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
    position = position_stack(vjust = 0.5),color = "black", size = 4) +
  scale_fill_manual(values = ir_source_colors) +
  labs(title="Water Source for Irrigation ",x="", y="% of HH") +
  theme_minimal(base_family = "serif")


##### [ir_source_own_or_public]
OPsource_colors <- c("lightblue3", "lightblue2" )
p2_source <- water_source %>%
  filter(variable == "ir_source_own_or_public") %>%
  ggplot(aes(x = ir_method, y = freq_percent, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            position = position_stack(vjust = 0.5),color = "black", size = 4) +
  scale_fill_manual(values = OPsource_colors) +
  labs(title = "Water Source | Own or Public",
       x = "",y = "% of HH" , fill = "" ) +
  theme_minimal(base_family = "serif")



grid.arrange(p1_source, p2_source, ncol = 2, widths = c(1.2, 1))
```

<br><br><br>

## Irrigation Pattern

```{r irrigation_pattern}

irrigation_pattern <- 
  df12_sugarcane %>% 
  select(ir_method,irri_times_month,irri_times_week,irri_hours,irri_days_between_ir) %>% 
  mutate(irri_days_between_ir=ifelse(ir_method=="Drip" & irri_days_between_ir>7,NA,irri_days_between_ir)) %>%
  pivot_longer(cols = -ir_method, names_to = "variable", values_to = "value") %>%
  group_by(variable,ir_method) %>%
   summarise(mean = mean(value, na.rm = TRUE),sd = sd(value, na.rm = TRUE),n = sum(!is.na(value)),se = sd / sqrt(n),ci_lower = mean - 1.96 * se,ci_upper = mean + 1.96 * se, .groups = "drop") %>% 
  filter(!is.na(sd))


# Define the order and new labels
ordered_vars <- c("irri_times_month","irri_times_week", "irri_hours", "irri_days_between_ir")
new_labels <- c("irri_times_week" = "IR per Week",
                "irri_times_month"= "IR per Month",    
                "irri_hours" = "Hours per IR",
                "irri_days_between_ir" = "Days Between IR")

pattern_drip <- irrigation_pattern %>% filter(ir_method=="Drip") %>% 
  ggplot(aes(x=factor(variable,levels=ordered_vars),y=mean,fill=variable)) +
  geom_bar(stat = "identity", width = 0.6,fill = "dodgerblue2") +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = round(mean, 2)),  position = position_stack(vjust = 0.5),color = "black", size = 4) +
  scale_x_discrete(labels = new_labels) +
  labs(title = "Drip Irrigation",x ="",y="") +
  theme_minimal(base_family = "serif") +theme(legend.position = "none")+
  scale_y_continuous(limits=c(0,15),breaks=seq(0,15,by=5))

pattern_flood <- irrigation_pattern %>% filter(ir_method=="Flood") %>% 
  ggplot(aes(x=factor(variable,levels=ordered_vars),y=mean,fill=variable)) +
  geom_bar(stat = "identity", width = 0.6, fill = "gray") +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = round(mean, 2)),  position = position_stack(vjust = 0.5),color = "black", size = 4) +
  scale_x_discrete(labels = new_labels) +
  labs(title = "Flood Irrigation",x ="",y="") +
  theme_minimal(base_family = "serif") + theme(legend.position = "none")+
  scale_y_continuous(limits=c(0,15),breaks=seq(0,15,by=5))

# grid.arrange(pattern_drip, pattern_flood, ncol=2, widths = c(1, 1), heights=c(1,1))


flood_in_drip_plot <- df2_sugarcane %>% 
  select(flood_before_after_drip,irri_months_drip_flood,
         irri_days_drip_flood,irri_hours_drip_flood)
  

p1_fl <- tibble::tribble(~Farm, ~flood_before_after_drip, ~n,
               "Drip farm",  "Flood and Drip",16,"Drip farm","Drip only",1) %>%
  mutate(freq_percent = n / sum(n) * 100) %>% 
  ggplot(aes(x = Farm, y = freq_percent, fill = flood_before_after_drip)) +
  geom_bar(stat = "identity") + 
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            position = position_stack(vjust = 0.5),color = "white", size = 4) +
  scale_fill_manual(values = c("Flood and Drip" = "dodgerblue4", "Drip only" = "dodgerblue2")) +
  labs(title = "Flood irrigation in plots \nirrigated with drip systems",x="",y="" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  theme(axis.text = element_blank(),axis.ticks = element_blank(),panel.grid = element_blank())


p2_fl <- flood_in_drip_plot %>%   select(-flood_before_after_drip) %>% 
  mutate(irri_days_drip_flood=
           ifelse(irri_days_drip_flood==11,NA,irri_days_drip_flood)) %>%
  rename("IR per Month"= irri_days_drip_flood ,
         "Hours per IR"= irri_hours_drip_flood,
         "Months in a Year" = irri_months_drip_flood) %>% 
  pivot_longer(cols = everything(),
               names_to = "variable", values_to = "value",values_drop_na = T) %>%
  group_by(variable) %>%
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE),n = sum(!is.na(value)),se = sd / sqrt(n),
            ci_lower = mean - 1.96 * se,ci_upper = mean + 1.96 * se, .groups = "drop") %>% 
  mutate(variable = factor(variable, levels = c("IR per Month","Hours per IR","Months in a Year"))) %>% 
  
  ggplot(aes(x = variable, y = mean, fill = variable)) +
  geom_bar(stat = "identity", width = 0.6,fill="dodgerblue2") +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = round(mean, 2)),  position = position_stack(vjust = 0.5),
            color = "black", size = 4) +
  labs(title = "Freq of flooding",x = "", y = "") +
  theme_minimal(base_family = "serif")

grid.arrange(pattern_drip, pattern_flood,p1_fl,p2_fl, ncol=2, nrow =2, heights=c(7,7))


```

<br><br><br>

## Sugarcane treatments

```{r  SC treat}

treat <- df12_sugarcane %>%
  select(uid, start,ir_method,insecticides_yn, fungi_yn, fertilze) %>% 
  mutate(start=as.Date(start)) %>% 
  mutate(fertilze = if_else(start < as.Date("2025-01-28"), NA_character_, fertilze)) %>% 
  arrange(fertilze) %>% 
  select(ir_method ,insecticides_yn ,fungi_yn ,fertilze)
treat$fungi_yn[treat$fungi_yn=="1"] <- "Yes"
treat$fungi_yn[treat$fungi_yn=="0"] <- "No"
treat$insecticides_yn[treat$insecticides_yn=="1"] <- "Yes"
treat$insecticides_yn[treat$insecticides_yn=="0"] <- "No"

treat1 <- treat %>% 
  pivot_longer(cols = -ir_method, names_to = "variable", values_to = "value") %>%
  count(variable,ir_method,value) %>% 
  filter(!is.na(value)) %>% 
  group_by(variable,ir_method) %>% mutate(freq_percent=n/sum(n)*100) 
treat1$variable[treat1$variable=="fungi_yn"] <- "Use Fungicides"
treat1$variable[treat1$variable=="insecticides_yn"] <- "Use Insecticides"


p1_treat <- treat1 %>%filter(variable == "fertilze") %>%
  mutate(value = factor(value, levels = c("fertigation", "manual_spread","both"))) %>% 
  ggplot(aes(x = ir_method, y = freq_percent, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            position = position_stack(vjust = 0.5),color = "white", size = 4) +
  labs(title = "Fertilization method",x = "",y = "% of HH" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  scale_fill_manual(
    values = c("manual_spread"="pink3","fertigation"="pink1","both"="pink4"),    
    labels = c("Fertigation","Manual spread","Both" ))


# Plot for "fungi_yn" "insecticides_yn
p2_treat <- treat1 %>%filter(variable != "fertilze",value=="Yes" ) %>%
  ggplot(aes(x = ir_method, y = freq_percent, fill = value)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            position = position_stack(vjust = 0.5),color = "black", size = 4) +
  facet_wrap(~variable, scales = "free_y") +
  labs(title = "",x = "",y = "" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  scale_fill_manual(values = c("Yes" = "pink3","No" = "white")) +
    scale_y_continuous(limits = c(0, 93), breaks = seq(0, 93, by = 25))+
  theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank()
)



grid.arrange(p1_treat, p2_treat, ncol = 2, widths = c(1, 1.1))


```


<br><br><br>

## Crop Other then Sugarcanes

```{r crop_bind}

p1_crop <- crop_bind %>% 
  filter(crop %in% c("Ginger","Wheat","Soybean")) %>% 
  mutate(crop_status =ifelse(crop_status =="drip","Drip Irrigated","Cutivated")) %>% 
  ggplot(aes(x = ir_method, y = freq_percent, fill = crop_status)) +
  geom_col() +facet_wrap(~ crop) +
  labs(title = "",x="",y = "% of HH ",fill = "") +
  theme_minimal(base_size = 14, base_family = "serif") +
  scale_fill_manual(
    values=c("Drip Irrigated" = "dodgerblue2", 
             "Cutivated" = "darkolivegreen3"))+
  theme(legend.position = "bottom")

p2_crop <- crop_bind %>% 
  filter(crop %in% c("Onion","Mango","Maize" )) %>% 
  mutate(crop_status =ifelse(crop_status =="drip","Drip Irrigated","Cutivated")) %>% 
  ggplot(aes(x = ir_method, y = freq_percent, fill = crop_status)) +
  geom_col() +facet_wrap(~ crop) +
  labs(title = "",x="",y = "% of HH ",fill = "") +
  theme_minimal(base_size = 14, base_family = "serif") +
  scale_fill_manual(
    values=c("Drip Irrigated" = "dodgerblue2", 
             "Cutivated" = "darkolivegreen3"))+
  theme(legend.position = "bottom")+
  scale_y_continuous(limits=c(0,40),breaks=seq(0,40,by=10))+
  theme(
  axis.title.y = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank()
)


p3_crop <- crop_bind %>% 
  filter(crop %in% c("Other" )) %>% 
  mutate(crop_status =ifelse(crop_status =="drip","Drip Irrigated","Cutivated")) %>% 
  ggplot(aes(x = ir_method, y = freq_percent, fill = crop_status)) +
  geom_col() +facet_wrap(~ crop) +
  labs(title = "",x="",y = "% of HH ",fill = "") +
  theme_minimal(base_size = 14, base_family = "serif") +
  scale_fill_manual(
    values=c("Drip Irrigated" = "dodgerblue2", 
             "Cutivated" = "darkolivegreen3"))

grid.arrange(p1_crop, p2_crop, ncol = 2, widths = c(1, 1))


```

<br><br><br>

## Economy

```{r economy}

# Plot 1: Sold Production (Ton)
p1_economy <- economy %>% filter(variable=="sold_ton_per_acre") %>% 
  ggplot(aes(x = ir_method, y = mean, fill = ir_method)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = paste0(round(mean))),vjust=7,size = 4) +
  labs(title = "Production Sold per Acre",x = "",y="Crop (Ton)") +
  theme_minimal(base_size = 14, base_family = "serif") +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  theme(legend.position = "none")


# Plot 0
blankPlot <- ggplot()+geom_blank(aes(1,1))+
  theme(
    plot.background = element_blank(), 
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(), 
   panel.border = element_blank(),
   panel.background = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_blank(),
   axis.text.x = element_blank(), 
   axis.text.y = element_blank(),
   axis.ticks = element_blank(),
   axis.line = element_blank()
     )

# Plot 2: expenses
p2_economy <- economy %>%
  filter(variable %in% c("expenses_total_per_acre", "expenses_labor_per_acre")) %>%
  mutate(variable = recode(variable, expenses_total_per_acre = "Total Expenses", 
                           expenses_labor_per_acre = "Labor Expenses")) %>%
  ggplot(aes(x = ir_method, y = mean, fill = ir_method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width=.2,color="black") +
  geom_text(aes(label = paste0(round(mean))),vjust=7,size = 4) +
  facet_wrap(~variable, scales = "free_y") +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  labs(title = "Expenses per Acre", x = "", y ="") +
  theme_minimal(base_family = "serif")+ 
  theme(legend.position = "none")

# Plot 3: Revenue
p3_economy <- economy %>% filter(variable=="revenue_per_acre") %>% 
  ggplot(aes(x = ir_method, y = mean, fill = ir_method)) +
  geom_col(width = 0.6) +
  geom_errorbar(aes(ymin=ci_lower,ymax=ci_upper),width = 0.2,color = "black") +
  geom_text(aes(label = paste0(round(mean))),vjust=7,size = 4) +
  labs(title = "Revenue per Acre",x = "",y="Thousands ₹") +
  theme_minimal(base_size = 14, base_family = "serif") +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  theme(legend.position = "none")


grid.arrange(p1_economy, blankPlot,  p3_economy,p2_economy,nrow = 2, ncol = 2, widths = c(1, 1.4))


```

<br><br><br>

## Opinion

```{r Opinion}

p1_op <- df2_sugarcane %>% 
  filter(!is.na(drip_more_less)) %>% 
  count(ir_method,drip_more_less) %>% 
  mutate(drip_more_less=ifelse(drip_more_less=="less","Less","More") ) %>% 
  group_by(ir_method) %>% mutate(freq_percent=n/sum(n)*100) %>% ungroup()  %>% 
    ggplot(aes(x = ir_method, y = freq_percent, fill = drip_more_less)) +
  geom_bar(stat = "identity") +     coord_flip() +
  geom_text(aes(label = paste0(round(freq_percent), "%\n", drip_more_less)),
            position = position_stack(vjust = 0.5),color = "white", size = 4) +
  scale_fill_manual(values = c("Less" = "dodgerblue4", "More" = "dodgerblue2")) +
  labs(title = "Opinion | Does drip cause more or less agricultural work? \nApart from deploying the pipes",
       x = "",y = "% of HH" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  theme(axis.ticks = element_blank(),panel.grid = element_blank(),
    legend.position = "none")

grid.arrange(p1_op, nrow=2, heights  = c(1, 1))



```



## installations | Farms with Drip-Irrigation

```{r installations}

#    first_drip_system .....
p2_op <- df2_sugarcane %>% 
  filter(!is.na(first_drip_system)) %>% 
  count(first_drip_system) %>% 
  mutate(freq_percent=n/sum(n)*100,
         first_drip_system=ifelse(first_drip_system==1,"Yes","No")) %>% 
  ggplot(aes(x = 1, y = freq_percent, fill = first_drip_system)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(freq_percent), "%\n", first_drip_system)),
            position = position_stack(vjust = 0.5),color = "white", size = 4) +
  scale_fill_manual(values = c("Yes" = "royalblue2", "No" = "gray60")) +
  labs(title = "Is it your first \ndrip system?",
       x = "",y = "" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  theme(axis.text = element_blank(),axis.ticks = element_blank(),panel.grid = element_blank(),
    legend.position = "none")+
  theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank()
)

# install_drip_year
p3_op <- df2_sugarcane %>% 
  select(uid, install_drip_year) %>%
  filter(!is.na(install_drip_year)) %>%
  count(install_drip_year) %>%
  mutate(freq_percent = round(100 * n / sum(n), 0)) %>%
  ggplot(aes(x = factor(install_drip_year), y = freq_percent, fill = factor(install_drip_year))) +
  geom_bar(stat = "identity", width = 0.6) +
  geom_text(aes(label = paste0(freq_percent, "%")),
            vjust = 1.15, color = "black", size = 4) +
  labs(title = "          Installation Year", x = "",y = "") +
  theme_minimal(base_family = "serif")+
  theme(legend.position = "none")+
  theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank()
)


why_drip<-
  df2_sugarcane %>% 
  filter(!is.na(why_drip)) %>% 
  select(starts_with("why_drip"),
         -why_drip,-`why_drip/other`, -`why_drip/hold_job_biz`)
why_drip_N <- as.numeric(count(why_drip))


p5_op <- why_drip %>% 
  pivot_longer(
    cols =everything(), names_to = "variable", values_to = "value") %>%
  count(variable,value) %>% 
  mutate(variable = sub(".*/", "", variable),
         freq_percent=(n/why_drip_N*100) ) %>% 
  filter(value != 0) %>% 
  ggplot(aes(x = factor(variable), y = freq_percent)) +
  geom_bar(stat = "identity", width = 0.6, fill = "dodgerblue4") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            vjust = 1.5, color = "white", size = 4) +
  labs(
    title = "What are the reasons you adopted drip irrigation?",
    x = "", y = "") +
  theme_minimal(base_family = "serif")+
  theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank()
)

# Plot 0
blankPlot <- ggplot()+geom_blank(aes(1,1))+
  theme(
    plot.background = element_blank(), 
   panel.grid.major = element_blank(),
   panel.grid.minor = element_blank(), 
   panel.border = element_blank(),
   panel.background = element_blank(),
   axis.title.x = element_blank(),
   axis.title.y = element_blank(),
   axis.text.x = element_blank(), 
   axis.text.y = element_blank(),
   axis.ticks = element_blank(),
   axis.line = element_blank()
     )








grid.arrange(p2_op, p3_op,  blankPlot,  p5_op ,nrow = 2, ncol = 2, widths =  c(1, 5))



```

```{r installations2}
#   plan_install_drip  -----
p4_op <- df2_sugarcane %>% 
  filter(!is.na(plan_install_drip)) %>% 
  count(plan_install_drip) %>% 
  mutate(freq_percent=n/sum(n)*100,
         plan_install_drip=ifelse(plan_install_drip==1,"Yes","No")) %>% 
  ggplot(aes(x = 1, y = freq_percent, fill = plan_install_drip)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(round(freq_percent), "%\n", plan_install_drip)),
            position = position_stack(vjust = 0.5),color = "white", size = 4) +
  scale_fill_manual(values = c("Yes" = "royalblue2", "No" = "gray60")) +
  labs(title = "Plan to install drip",
       x = "",y = "" , fill = "" ) +
  theme_minimal(base_family = "serif") + 
  theme(axis.text = element_blank(),axis.ticks = element_blank(),panel.grid = element_blank(),legend.position = "none")


#      plan_install_drip_why_not
#      For what reasons you don't want drip?
plan <- 
  df2_sugarcane %>% select(plan_install_drip_why_not) %>% 
  filter(!is.na(plan_install_drip_why_not))

plan$no_plan_drip[plan$plan_install_drip_why_not %in% c(
  "Money issues","Expenses","Money")] <- "Lack of Capital"
plan$no_plan_drip[plan$plan_install_drip_why_not %in% c(
  "Dam water is near by","Dam water near to","River is close and he have only one acres")] <- "I Have Water"

plan_not <- plan %>% 
  count(no_plan_drip) %>% 
  mutate(freq_percent=n/sum(n)*100) 
plan_not_N <- sum(plan_not$n)

p5_op <- plan_not %>% 
  ggplot(aes(x = factor(no_plan_drip), y = freq_percent)) +
  geom_bar(stat = "identity", width = 0.6, fill = "gray60") +
  geom_text(aes(label = paste0(round(freq_percent), "%")),
            vjust = 1.5, color = "white", size = 4) +
  labs(title = "           For what reasons you don't want drip?",x = "", y = "% of HH") +
  theme_minimal(base_family = "serif") +
  theme(legend.position = "none")


grid.arrange(p4_op,p5_op, ncol=2, widths = c(1, 5))

```


```{r job_biz}

job_biz <- df2_sugarcane %>%
  select(uid,ir_method, job_biz_income, job_biz_less,plan_install_drip_prevent_jobBiz,plan_install_drip_why_not_jobBiz) 

p1_jb <- job_biz %>% filter(!is.na(job_biz_income)) %>% 
  group_by(ir_method) %>% summarise(freq_percent=mean(job_biz_income )*100) %>% 

  ggplot(aes(x = ir_method, y = freq_percent,fill = ir_method)) +
  geom_bar(stat = "identity") +     coord_flip() +
  geom_text(aes(label = paste0(round(freq_percent), "%\n")),
            position = position_stack(vjust = 0.5),color = "black", size = 4) +
  labs(title = "Do you have income from a salary job or non-farming business in addition to selling crops?",
              subtitle = "fraction of farmers said YES",x = "",y = ""  ) +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  theme_minimal(base_family = "serif") + 
  theme(axis.ticks = element_blank(),panel.grid = element_blank(),legend.position = "none")

p2_jb <-job_biz %>% filter(!is.na(job_biz_less)) %>% 
  group_by(ir_method) %>% summarise(freq_percent=mean(job_biz_less )*100) %>% 

  ggplot(aes(x = ir_method, y = freq_percent,fill = ir_method)) +
  geom_bar(stat = "identity") +     coord_flip() +
  geom_text(aes(label = paste0(round(freq_percent), "%\n")),
            position = position_stack(vjust = 0.5),color = "black", size = 4) +
  labs(title = "Are you holding the job/business because drip causes LESS work?",subtitle = "fraction of farmers said YES",x = "",y = ""  ) +
  scale_fill_manual(values = c("Drip" = "dodgerblue3", "Flood" = "gray")) +
  theme_minimal(base_family = "serif") + 
  theme(axis.ticks = element_blank(),panel.grid = element_blank(),
        legend.position = "none")
  

grid.arrange(p1_jb,p2_jb, nrow=2, heights  = c(1, 1))



```

**Are you concerned that drip will prevent you from holding a job/business?**
ir_method==Flood & ${job_biz_income} = '1' 
and plan_install_drip} = '1' 


**Do you think using drip will prevent you from holding your job/business?**
ir_method==Flood & ${job_biz_income} = '1' 
${plan_install_drip} = '0' 
         
         
```{r instions2}



```

This is some text.

<br>

This is text after an empty line.

\bigskip % a bit of vertical space

\medskip % slightly less space

\vspace{1cm}

\% custom space
