---
title: "Irrigation"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
library(formattable)
library(knitr)
library(MatchIt)
library(tableone)
library(gridExtra)


water_use_6.2 <- read.csv("~/R/Saptari/data/water_use_6.2.csv")

water01 <- read.csv("~/R/Saptari/data/water01.csv")

```


 | Daily Monitoring Excel | Survey Section 6.2 | Survey Section 5 |
  |------------ | -------------|------------ |
 ||Water Extraction Mechanisms |Land|

# Irrigation hours YEAR saptari
```{r Irrigation hours YEAR saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}
pump_water_use_6.2_hr <- water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="Saptari",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(district, year) %>% 
  summarise_at(c("Yearly_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round))

ggplot(data=pump_water_use_6.2_hr, aes(x=year, y=Yearly_hr, fill=year)) +
  geom_bar(stat="identity")+
  geom_text(aes(label = Yearly_hr, group = year),
            position = position_dodge(0.8),
            vjust = 1.2, size = 4.5, color = "white")+
  ggtitle("Saptari")+
  xlab(" ") +
  ylab("Hours") +
  theme(legend.position = "none",plot.title = element_text(size = rel(2), hjust = 0.5))

```

# Irrigation hours YEAR Rautahat Bara Sarlahi
```{r Irrigation hours YEAR Rautahat Bara Sarlahi, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}
R_pump_water_use_6.2_hr <- water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="RSB",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(district, year) %>% 
  summarise_at(c("Yearly_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round))

ggplot(data=R_pump_water_use_6.2_hr, aes(x=year, y=Yearly_hr, fill=year)) +
  geom_bar(stat="identity")+
  geom_text(aes(label = Yearly_hr, group = year),
            position = position_dodge(0.8),
            vjust = 1.2, size = 4.5, color = "white")+
  ggtitle("Rautahat Bara Sarlahi")+
  xlab(" ") +
  ylab("Hours") +
  theme(legend.position = "none",plot.title = element_text(size = rel(2), hjust = 0.5))+  scale_x_continuous(breaks=seq(2018,2019,1))

```

***

# Pump use houres
Some of the pumps were operating thae same day - therefore the sum from the three pumps is more than 100%  
 **p1_hr** is the Primary pump SPIP in midline and endline  

# Pump use - houres in a YEAR saptari  
```{r Primary pump use YEAR saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="Saptari",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(year) %>% 
  summarise_at(c("p1_hr","p2_hr","p3_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round))


```

# Pump use - houres in a YEAR Rautahat Bara Sarlahi
```{r Primary pump use YEAR Rautahat Bara Sarlahi, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="RSB",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(year) %>% 
  summarise_at(c("p1_hr","p2_hr","p3_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round))

```

***

 
 
 

# Irrigation days YEAR saptari
```{r Irrigation days YEAR saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```


# Irrigation days YEAR Rautahat Bara Sarlahi
```{r Irrigation days YEAR Rautahat Bara Sarlahi, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```

***

# Pump use days
Some of the pumps were operating thae same day - therefore the sum from the three pumps is more than 100%  
 **p1_hr** is the Primary pump SPIP in midline and endline  
 





# By seasons
***

# Irrigation hours season saptari
```{r Irrigation hours season saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

SAPTARI_season_water_use_6.2_hr <- water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="Saptari",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(district, year) %>% 
  summarise_at(c("Monsoon_hr","Winter_hr","Summer_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round)) %>% 
  arrange( desc(district))

SAPTARI_season_water_use_6.2_hr <- 
  gather(SAPTARI_season_water_use_6.2_hr, key="measure", value="Hours", c("Monsoon_hr","Winter_hr","Summer_hr"))


ggplot(data=SAPTARI_season_water_use_6.2_hr, aes(x=year, y=Hours, fill=year)) +
  geom_bar(stat="identity")+
  facet_wrap(~measure)+
  geom_text(aes(label = Hours, group = year),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white")+
  ggtitle(" ")+
  xlab(" ") +
  theme(legend.position = "none",plot.title = element_text(size = rel(1.5), hjust = 0.5))

```

# Irrigation hours season Rautahat Bara Sarlahi 
```{r Irrigation hours season Rautahat Bara Sarlahi , echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}
RSB_season_water_use_6.2_hr <- water_use_6.2 %>% 
  filter(TreatmentControl== "Treatment",district=="RSB",
         !household_questionnaire_id %in% c("T308707002" ,"T301911010")) %>% 
  group_by(district, year) %>% 
  summarise_at(c("Monsoon_hr","Winter_hr","Summer_hr"), mean, na.rm = TRUE) %>% 
  mutate(across(is.numeric,round)) %>% 
  arrange( desc(district))

RSB_season_water_use_6.2_hr <- 
  gather(RSB_season_water_use_6.2_hr, key="measure", value="Hours", c("Monsoon_hr","Winter_hr","Summer_hr"))


ggplot(data=RSB_season_water_use_6.2_hr, aes(x=year, y=Hours, fill=year)) +
  geom_bar(stat="identity")+
  facet_wrap(~measure)+
  geom_text(aes(label = Hours, group = year),
            position = position_dodge(0.8),
            vjust = 1.5, size = 4.5, color = "white")+
  ggtitle(" ")+
  xlab(" ") + ylab(" ") +
  theme(legend.position = "none",plot.title = element_text(size = rel(1.5), hjust = 0.5))+  scale_x_continuous(breaks=seq(2018,2019,1))

```

***

# Irrigation days season saptari
```{r Irrigation days season saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```

# Irrigation days season Rautahat Bara Sarlahi
```{r Irrigation days season Rautahat Bara Sarlahi, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```

***


 | Daily Monitoring Excel | Survey Section 6.2 | Survey Section 4.9 |
  |------------ | -------------|------------ |
 ||Water Extraction Mechanisms |Agriculture|

# Irrigated land YEAR saptari
```{r Irrigated land YEAR saptari, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```

# Irrigated land YEAR Rautahat Bara Sarlahi
```{r Irrigated land YEAR Rautahat Bara Sarlahi, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, out.width="33%", paged.print=FALSE}

```

***
***

# Daly monitoring timeline
### X-axis - daily with season marking
### 1. Number of hours of irrigating daily
```{r hours of irrigating daily, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, paged.print=FALSE}

```

### 2. The number of farmers who watered each day
```{r The number of farmers who watered each day, echo=FALSE, fig.height=3, fig.width=5, message=FALSE, warning=FALSE, paged.print=FALSE}

```


```{r Daily frequency of households who irrigate, echo=FALSE, fig.align='center', message=FALSE, warning=FALSE, paged.print=FALSE}

Hours_by_day <- water01 %>% 
  group_by(season,date) %>% 
  summarise(Hours=mean(Hours)) 


ggplot(data = Hours_by_day, aes(x = date, y = Hours))+
  labs(title="Avg. irrigation hours for SPIP households")+
  geom_line(color = "#00AFBB", size = 0.5)+
  stat_smooth(color = "#FC4E07", fill = "#FC4E07",metho = "loess")

Hours_by_day <- water01 %>% 
  group_by(season,date) %>% 
  summarise(Hours=mean(Hours)) 


ggplot(data = Hours_by_day, aes(x = date, y = Hours))+
  labs(title="Avg. irrigation hours for SPIP households")+
  geom_line(color = "#00AFBB", size = 0.5)+
  stat_smooth(color = "#FC4E07", fill = "#FC4E07",metho = "loess")




```








