---
title: "Ramthal Midline 2022 Survey"
author: "Renew Version, Started on December 19, 2022"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: pdflatex
---

```{r setup, include=FALSE}

library(tidyverse)
library(knitr)
library(tinytex)
library(kableExtra)
library(haven)
Adt_211222 <- read_dta("C:/Users/Dan/Downloads/Adt_raw_21 Dec 2022.dta")
Adt_24_12_22 <- read_dta("C:/Users/Dan/Downloads/Anonymized_Dataset_raw_24 Dec 2022.dta")

Adt  <- Adt_211222 %>% mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control"))
Adt3 <- Adt_24_12_22 %>% mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control"))


adt <- Adt_211222 %>% 
  mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control")) %>% filter(Grp=="treatment")

adt3 <- Adt_24_12_22 %>% 
  mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control")) %>% filter(Grp=="treatment")

knitr::opts_chunk$set(echo = TRUE)
```



```{r Grp, echo=F}
 
 dt <- Adt_24_12_22 %>% 
   mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control")) %>% 
   select(id,Grp)
 
df_df <- Adt_211222 %>% 
   mutate(Grp=ifelse(grepl('1', mm2), "treatment", "control")) %>% 
   select(id,Grp) %>% bind_rows(dt) %>% 
   count(Grp) %>% arrange(desc(Grp))


kbl(df_df) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

  
```




&nbsp;

**mm5** Have you ever (even once) made any use of this water for irrigating your land?
```{r mm5, echo=F}

dt5 <- adt3%>%select(Grp,mm5)

dt_dt5 <- adt %>%select(Grp,mm5)%>% bind_rows(dt5)%>% count(Grp,mm5)%>%select(2:3)%>%mutate(mm5=ifelse(mm5==1,"Yes","No"))%>%arrange(desc(mm5))

kbl(dt_dt5) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mm9** How many farmers are there between you and the valve/pipeline?
```{r mm9, echo=F}

dt9 <- adt3%>%select(Grp,mm9)

dt_dt9 <- adt %>%select(Grp,mm9)%>% bind_rows(dt9)%>%
  count(Grp,mm9)%>%select(2:3)%>% rename(farmers_B4_me=mm9)

kbl(dt_dt9) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

```

&nbsp;

#### **Use of Water from the Project**

&nbsp;

**mm10**		Has it ever happened to you that farmers "before" you have used up a lot of the water from the pipe, so you did not have enough?
```{r table_mm10, echo=FALSE}

dt10 <- adt3%>%select(Grp,mm10)

dt_dt10 <- adt %>%select(Grp,mm10)%>% bind_rows(dt10)%>%
  count(Grp,mm10)%>%
  mutate(a=case_when(
    mm10==1 ~  "1 It has never happened",
    mm10==2 ~  "2 It happens about once a season",
    mm10==3 ~  "3 It happens several times a season",
    mm10==4 ~  "4 It happens on a constant basis",
    mm10==5 ~  "5 Some seasons it happens and some it doesn't",
    TRUE ~ "na")) %>% 
  filter(!is.na(mm10)) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(a,n,freq)

kbl(dt_dt10) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

```

&nbsp;

**mw2**	Have you used it in [ _____ ]?
```{r mw2, echo=F}

dt2w <- adt3%>%select(Grp,mw2)

dt_dt2w <- adt %>%select(Grp,mw2)%>% bind_rows(dt2w)%>%
    count(Grp,mw2)%>%select(2:3)%>%
    mutate(mw2=ifelse(mw2==1,"Kharif",ifelse(mw2==2,"Rabi", "Both")))

kbl(dt_dt2w) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")


```

&nbsp;

**mw1a** If Yes, in which year did you first make use of the water?
```{r table_mw1a, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

dtwmw1a <- adt3%>%select(Grp,mw1a)

dt_dtwmw1a <- adt %>%select(Grp,mw1a)%>% bind_rows(dtwmw1a)%>%
  count(Grp,mw1a)%>%select(2:3)

  kable(dt_dtwmw1a) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw1b**In what season did you use it in that year?
```{r mw1b, echo=F}

dtmw1b <- adt3%>%select(Grp,mw1b)

dt_dtmw1b <- adt %>%select(Grp,mw1b)%>% bind_rows(dtmw1b)%>%
  count(Grp,mw1b)%>%select(2:3)%>%
  mutate(mw1b=ifelse(mw1b==1,"Kharif","Rabi"))

  kable(dt_dtmw1b) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw1c** "If No, Why? (Multiple choice)
```{r mw1c, echo=F}

dtmw1c <- adt3%>%  select(mw1c_1:mw1c_10)

dt_dtmw1c <- adt %>%select(mw1c_1:mw1c_10)%>% bind_rows(dtmw1c)%>%
    summarize_if(is.numeric, sum, na.rm=TRUE) %>% 
  gather("mw1c","n") %>% 
  mutate(Q=c("The main piping was never functional",
             "The laterals was never installed in my field",
             "The laterals in my field was damaged",
             "Rainfall was sufficient",
             "I wanted to irrigate, but other farmers took all the water",
             "Water was supplied only after I already sowed a rainfed crop",
             "Water was not supplied when needed",
             "I did not know when water was supplied",
             "I do not trust the company",
             "Water supply is unpredictable I cant count on it"
  ), .before=mw1c) %>%  select(Q,n)

  kable(dt_dtmw1c) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw4** Are you still making use of the water from the project to irrigate your land?"
```{r mw4,echo=FALSE}

dtmw4 <- adt3%>%  select(Grp,mw4)

dt_dtmw4 <- adt %>%select(Grp,mw4)%>% bind_rows(dtmw4)%>%
  count(Grp,mw4)%>%select(2:3)%>%
  mutate(Q=c("1 Yes, Everytime Water is provided",
             "2 No, I stopped, even if water is provided",
             "3 Sometimes, Depends",NA
  ), .before=mw4) %>% 
  filter(!is.na(Q)) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(-c(mw4,sumA))

  kable(dt_dtmw4) %>% kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw4b**		If *No* or *Sometimes* What was the last year you use of the water?
```{r mw4b, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

dtmw4b <- adt3%>%  select(Grp,mw4b)

dt_dtmw4b <- adt %>%select(Grp,mw4b)%>% bind_rows(dtmw4b) %>% 
    count(Grp,mw4b)%>%select(2:3)

kable(dt_dtmw4b) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw5 mw6**		How many years in total did you ever make use of the water for irrigation during ____ ?
```{r mw5mw6,echo=FALSE}

dtmw5mw6 <- adt3%>% select(Grp,mw5,mw6) 

dt_dtmw5mw6  <- adt %>%select(Grp,mw5,mw6) %>% bind_rows(dtmw5mw6)%>%
  gather("season","toat_years",-Grp) %>% 
  count(Grp,season,toat_years)%>%select(2:4)%>%
  mutate(season=ifelse(season=="mw5","Kharif","Rabi"))

kable(dt_dtmw5mw6) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**m20**		Can you indicate in which years and seasons you ever make use of the water for irrigation?
```{r m20,echo=FALSE} 
dtm20 <- adt3%>% select(Grp,starts_with("m20_") )

dt_dtm20  <- adt %>% select(Grp,starts_with("m20_") ) %>% bind_rows(dtm20)%>%
  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
  gather("m20","n") %>% arrange(m20)
  kable(dt_dtm20) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw7	mw9**	In Kharif/Rabi, when you did **NOT** irrigate, what are the reasons? (Multiple choice)   

The most frequent answers:   
[3]	Rainfall was sufficient  
[4]	I wanted to irrigate, but company did not supply water   
[7]	Water was not supplied when needed  

```{r mw7_mw9,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}

dtmw_7_9 <- adt3 %>%select(Grp,starts_with("mw7"),starts_with("mw9") ) 

mw_7_9<- adt %>%select(Grp,starts_with("mw7"),starts_with("mw9") ) %>% bind_rows(dtmw_7_9)%>%
  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
  gather("mw","n")

mw_7_9$mw = substring(mw_7_9$mw, 5)
mw_7_9 <-mw_7_9 %>%separate(mw,c("season" ,"year","a"),sep="_")
mw_7_9 <-mw_7_9 %>% 
  group_by(season,year) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  filter(a %in% c("3","4","7"))%>% 
  select(-c(n,sumA)) %>% 
  spread(year, freq)
  
kable(mw_7_9) %>% kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw12**		Typically, in your experience, when water is provided in a particular year, in which month does it start?
```{r mw12,echo=FALSE} 

dtmw12 <- adt3%>%  select(id,Grp,starts_with("mw12"))

dt_dtmw12 <- 
  adt %>%select(id,Grp,starts_with("mw12") ) %>% bind_rows(dtmw12) %>%
  count(mw12) %>% 
  mutate(month=case_when(
    mw12==1~ "January",mw12==2~"February",mw12==3~ "March",
    mw12==4~ "April",mw12==5~ "May",mw12==6~ "June",
    mw12==7~ "July",mw12==8~ "August",mw12==9~ "September",
    mw12==10~ "October",mw12==11~ "November",mw12==12~ "December",TRUE ~ 'dont know')) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(month,n,freq)

  kable(dt_dtmw12) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw13**		Typically, in your experience, when water is provided in a particular year, in which month does it end for the year?
```{r mw13,echo=FALSE} 

dtmw13 <- adt3%>%  select(id,Grp,starts_with("mw13"))

dt_dtmw13 <- 
  adt %>%select(id,Grp,starts_with("mw13") ) %>% bind_rows(dtmw13) %>%
  count(mw13) %>%
  mutate(month=case_when(
    mw13==1~ "January",mw13==2~ "February",mw13==3~ "March",
    mw13==4~ "April",mw13==5~ "May",mw13==6~ "June",
    mw13==7~ "July",mw13==8~ "August",mw13==9~ "September",
    mw13==10~ "October",mw13==11~ "November",mw13==12~ "December",TRUE ~ 'dont know')) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(month,n,freq)

  kable(dt_dtmw13) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

**mw14**		Typically, in your experience, during the period water is provided, how often is it provided?
```{r mw14,echo=FALSE} 

dtmw14 <- adt3%>%  select(id,Grp,starts_with("mw14"))

dt_dtmw14 <- adt %>%select(id,Grp,starts_with("mw14") ) %>% bind_rows(dtmw14) %>%
  count(mw14)%>% 
  mutate(a=case_when(
    mw14==1~ "Every _____ Days",
    mw14==2~ "Very unpredictable and irreular",
    mw14==4~ "Water never Provided]",
    TRUE ~ 'dont know')) %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(a,n,freq)

kable(dt_dtmw14) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")


adt %>%select(id,Grp,starts_with("mw14") ) %>% bind_rows(dtmw14) %>% 
  filter(!is.na(mw14_int)) %>% 
  select(id,mw14_int)%>% 
  rename("Every _____ Days"=mw14_int) %>% 
  kable() %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")
```

&nbsp;

&nbsp;

#### **Damaged irrigation system**  
**m35** What is the status of the main pipe coming into your land ?
```{r m35,echo=FALSE} 

dtm35 <- adt3%>%  select(id,Grp,m35)

dt_dtm35 <- adt %>%select(id,Grp,m35) %>% bind_rows(dtm35) %>%
  count(m35)%>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  select(-sumA) %>% 
  mutate(m35=ifelse(m35==1,"Works",ifelse(m35==2,"Damaged",NA)))

kable(dt_dtm35) %>% kable_classic(full_width = F,html_font = "Cambria",position = "left")
```

&nbsp;

**m35a** What caused the damage?
```{r m35a,echo=FALSE} 

dtm35a <- adt3%>%  select(Grp,starts_with("m35a"))

dt_dtm35a <- adt %>%select(Grp,starts_with("m35a") ) %>% bind_rows(dtm35a) %>%
  summarize_if(is.numeric, sum, na.rm=TRUE) %>%
  gather("mw","n") %>% 
  mutate(sumA=sum(n)) %>% 
  mutate(freq = paste0(round(100 * n/sumA, 0), "%")) %>% 
  mutate(a=case_when(
    mw== "m35a_1"~ "Animals that graze in the field",
    mw=="m35a_2"~ "Rodents",
    mw=="m35a_3"~ "Machinery like tractors or threshers",
    mw=="m35a_4"~ "Thieves",
    mw=="m35a_5"~ "Other Farmers",
    mw=="m35a_6"~ "Damaged during operation",
    TRUE ~ "Company")) %>% 
  select(a,n,freq)

kable(dt_dtm35a) %>% kable_classic(full_width = F,html_font="Cambria",position = "left")
```

&nbsp;

**m35b** How long has the main pipes been damaged?
```{r m35b,echo=FALSE} 
dtm35b <- adt3%>%  mutate(m35b_year=m35b_year*12) %>% 
  select(id,m35b_month,m35b_year)

dt_dtm35b <- adt %>% mutate(m35b_year=m35b_year*12) %>%
  select(id,m35b_month,m35b_year) %>% bind_rows(dtm35b) %>%
  summarise(m35b=m35b_month+m35b_year) %>%
  summarise(m35b=mean(m35b,na.rm = T)) %>% 
  mutate_at(1,round,2) %>% 
  mutate("Average"= sub("^(.*)$", "\\1 month", m35b)) %>% select(-1)

kable(dt_dtm35b) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

```

&nbsp;

**m35c** What is the status of the laterals?
```{r m35c,echo=FALSE} 

dtm35c <-adt3 %>% select(id,Grp,m35c)

dt_dtm35c <- adt %>% select(id,Grp,m35c)%>% bind_rows(dtm35c) %>%
  count(m35c)%>% 
  mutate(m35c=
           ifelse(m35c==1,"Works, laid in the field",
                  ifelse(m35c==2,"OK, but in storage","Damaged")))

kable(dt_dtm35c) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

```

&nbsp;

**L7** What irrigation source are you dependent on? (Rank according to the degree of importance)
```{r L7,echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
ans <- data.frame(
  Grp = c ("control","control","control","control","control","control",
           "treatment","treatment","treatment","treatment","treatment","treatment"),
  op = c (2,3,4,5,-888,NA,
          2,3,4,5,-888,NA), 
  source = c("Tank","Open well","Borewell","Government water supply","Other (Rain)","non",
             "Tank","Open well","Borewell","Government water supply","Other (Rain)","non"))

dtl7_rank_1 <- Adt3 %>%select(id,Grp,starts_with("l7_"))
  
l7_rank_1 <- Adt %>%select(id,Grp,starts_with("l7_")) %>% bind_rows(dtl7_rank_1)%>%
  count(Grp,l7_rank_1) %>% 
  rename(op=l7_rank_1,n_rank_1=n) %>% 
  full_join(ans) %>% 
  arrange(desc(Grp))

l7_rank <- Adt %>%select(id,Grp,starts_with("l7_")) %>% bind_rows(dtl7_rank_1)%>%
    count(Grp,l7_rank_2) %>%
  rename(op=l7_rank_2,n_rank_2=n) %>% 
  full_join(l7_rank_1) %>% 
  arrange(desc(Grp) ) %>% 
  group_by(Grp) %>%
  mutate(sumA=sum(n_rank_1,na.rm = T)) %>% 
  mutate(rank_1_freq_in_group = paste0(round(100 * n_rank_1/sumA, 0), "%"),
         rank_2_freq_in_group = paste0(round(100 * n_rank_2/sumA, 0), "%")) %>% 
  mutate(rank_1_freq_in_group=ifelse(n_rank_1=="NA%",NA,rank_1_freq_in_group),
         rank_2_freq_in_group=ifelse(n_rank_2=="NA%",NA,rank_2_freq_in_group)) %>% 
  select(Grp,source,n_rank_1,rank_1_freq_in_group,n_rank_2,rank_2_freq_in_group)

kable(l7_rank) %>%  kable_classic(full_width = F, html_font = "Cambria",position = "left")

```


#### fix












