---
title: "Crop maps of Rabi and Kharif 2017-2019"
author: "According to data collected by Jain Irrigation Systems Ltd."
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gridExtra)

library(readr)
jain_common_crop <- read_csv("~/master_research/DATAs/ramthal_data/jain_common_crop.csv")
jain_highvalue_crop <- read_csv("~/master_research/DATAs/ramthal_data/jain_highvalue_crop.csv")
ramthal_east_tidy2 <- read_csv("~/master_research/DATAs/ramthal_data/ramthal_east_tidy2.csv")

group.colors <- c(Cereals="tan3",
                  Oilseeds= "khaki1",
                  Pulses= "indianred3",
                  Vegetables= "olivedrab3",
                  Others= "lightskyblue3")

```

## Common Crop

Every plot combine several types of crop. The following map signs the most dominant crop in any plot.
Crops were grouped into categories of cereals, pulses, vegetables, oilseeds, and 'other' . The gray areas are plots with no data. The crop list appears at the end of the report.
Rabi seasons maps are shown first, followed by the Kharif seasons.


#grid.arrange(hhh , ggg , ncol=2)
```{r pressure0, echo=FALSE}

rabbi_2017 <- 
  jain_common_crop %>% filter(season == "rabbi_2017") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+theme(legend.position="none")+ 
  scale_fill_manual(values=group.colors)

rabbi_2018 <- 
  jain_common_crop %>% filter(season == "rabbi_2018") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+theme(legend.position="none")+ 
  scale_fill_manual(values=group.colors)

rabbi_2019 <- 
  jain_common_crop %>% filter(season == "rabbi_2019") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+theme(legend.position="none")+ 
  scale_fill_manual(values=group.colors)

grid.arrange(rabbi_2017 , rabbi_2018 , rabbi_2019 , ncol=3)

```



## Rabi 2017

```{r pressure1, echo=FALSE}

jain_common_crop %>% filter(season == "rabbi_2017") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

## Rabi 2018

```{r pressure2, echo=FALSE}
jain_common_crop %>% filter(season == "rabbi_2018") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

## Rabi 2019

```{r pressure3, echo=FALSE}

jain_common_crop %>% filter(season == "rabbi_2019") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

## Kharif 2017

```{r pressure4, echo=FALSE}

jain_common_crop %>% filter(season == "kharif_2017") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

## Kharif 2018

```{r pressure5, echo=FALSE}
jain_common_crop %>% filter(season == "kharif_2018") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

## Kharif 2019

```{r pressure6, echo=FALSE}

jain_common_crop %>% filter(season == "kharif_2019") %>% right_join(ramthal_east_tidy2) %>% 
  ggplot(aes(x = long, y = lat, group = group, fill = cropCat)) +
  geom_polygon() +
  geom_path(color = "white", size = 0.2) +
  coord_equal() +
  theme(axis.title = element_blank(), axis.text = element_blank()) +
  labs(x = " ",y = " ",fill = " ")+
  theme_minimal()+
  scale_fill_manual(values=group.colors)

```

